%
% FH Technikum Vienna
% !TEX encoding = UTF-8 Unicode
%
% Creation of Master and Bachelor theses at the FH Technikum Wien using LaTeX and the TWBOOK class
%
% To create your own document you have to add the following:
% 1) Set[...] with \documentclass: Master's or Bachelor's thesis, course of study and language.
% 2) With \newcommand{\FHTWCitationType}. Set citation standard (is usually given by the study program - please ask)
% 3) fill in cover sheet, abstract, etc.
% 4) and write the paper (enter the used literature sources in Literatur.bib)
%
% Tested with TeXstudio with character encoding ISO-8859-1 (=ansinew/latin1) and MikTex under Windows
% Note that the encoding of the file matches the encoding of the package inputenc!
% The encoding of the file twbook.cls MUST be ANSI!
% When using UTF8 not only the encoding of the document must be set to UTF8, but also the encoding of the BibTex file!
%
% Please send bugreports and feedback via email to latex@technikum-wien.at
%
% Versions
% *) V0.7: 9.1.2015, RO: modeline adjusted and moved
% *) V0.6: 10.10.2014, RO: Further adaptation to UK
% *) V0.5: 8.8.2014, WK: Literature sources revised and adapted
% *) V0.4: 4.8.2014, WK: Inital version imported into SVN
%
\documentclass[MSE,Master,english]{twbook}%\documentclass[Bachelor,BMR,ngerman]{twbook}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

%
% Hier biblatex & Biber konfigurieren; Vergessen Sie nicht, dass Sie biber verwenden müssen um eine Bibliothek zu erzeugen
%
\usepackage[backend=biber, style=numeric]{biblatex}
\addbibresource{Literatur.bib}

%
% Bei Bedarf bitte hier die Syntax-Highlightings anpassen
%
\usepackage[final]{listings}
\lstset{captionpos=b, numberbychapter=false,caption=\lstname,frame=single, numbers=left, stepnumber=1, numbersep=2pt, xleftmargin=15pt, framexleftmargin=15pt, numberstyle=\tiny, tabsize=3, columns=fixed, basicstyle={\fontfamily{pcr}\selectfont\footnotesize}, keywordstyle=\bfseries, commentstyle={\color[gray]{0.33}\itshape}, stringstyle=\color[gray]{0.25}, breaklines, breakatwhitespace, breakautoindent}
\lstloadlanguages{[ANSI]C, C++, [gnu]make, gnuplot, Matlab}

%Formatieren des Quellcodeverzeichnisses
\makeatletter
% Setzen der Bezeichnungen für das Quellcodeverzeichnis/Abkürzungsverzeichnis in Abhängigkeit von der eingestellten Sprache
\providecommand\listacroname{}
\@ifclasswith{twbook}{english}
{%
    \renewcommand\lstlistingname{Code}
    \renewcommand\lstlistlistingname{List of Code}
    \renewcommand\listacroname{List of Abbreviations}
}{%
    \renewcommand\lstlistingname{Quellcode}
    \renewcommand\lstlistlistingname{Quellcodeverzeichnis}
    \renewcommand\listacroname{Abkürzungsverzeichnis}
}
% Wenn die Option listof=entryprefix gewählt wurde, Definition des Entyprefixes für das Quellcodeverzeichnis. Definition des Macros listoflolentryname analog zu listoflofentryname und listoflotentryname der KOMA-Klasse
\@ifclasswith{scrbook}{listof=entryprefix}
{%
    \newcommand\listoflolentryname\lstlistingname
}{%
}
\makeatother
\newcommand{\listofcode}{\phantomsection\lstlistoflistings}

% Die nachfolgenden Pakete stellen sonst nicht benötigte Features zur Verfügung
\usepackage{blindtext}

%
% Einträge für Deckblatt, Kurzfassung, etc.
%
\title{Transparency in\\Decentraland DAO}
\author{Comerci Wolcanyik, Nicol{\'a}s}
\studentnumber{2120299002}
%\author{Titel Vorname Name, Titel\and{}Titel Vorname Name, Titel}
%\studentnumber{XXXXXXXXXXXXXXX\and{}XXXXXXXXXXXXXXX}
\supervisor{Dinhof, Gerhard}
%\supervisor[Begutachter]{Titel Vorname Name, Titel}
%\supervisor[Begutachterin]{Titel Vorname Name, Titel}
%\secondsupervisor{Titel Vorname Name, Titel}
%\secondsupervisor[Begutachter]{Titel Vorname Name, Titel}
%\secondsupervisor[Begutachterinnen]{Titel Vorname Name, Titel}
\place{Vienna}
\outline{\toComplete}
\keywords{Keyword1, Keyword2, Keyword3, Keyword4}
\acknowledgements{\toComplete}

\begin{document}

\maketitle

%
% .. und hier beginnt die eigentliche Arbeit. Viel Erfolg beim Verfassen!
%
\chapter{Introduction}
From October 31, 2008 (when the Bitcoin whitepaper was published) to the present day, people's interest in Blockchain technology has been growing progressively and increased exponentially from 2020 onwards. 

There are a large number of projects that rely on this technology to date, one of them is Decentraland: a 3D digital world that will be discussed in the next section and that uses Ethereum to execute its transactions.

One of the great advantages of Blockchain is transparency: anyone can verify all transactions made, from the first to the last. But how easy is it for an average user to access this information? What kind of analysis and conclusions can be drawn once obtained? This paper will seek to answer these questions specifically using Decentraland's DAO as the object of study.
\clearpage

\chapter{Basics}
\section{Blockchain}
Today there are different types of blockchain, but based on the original concept and taking as a reference the article \emph{"La blockchain: fundamentos, aplicaciones y relaci{\'o}n con otras tecnolog{\'\i}as disruptivas"}\cite{blockchain}, it was created to store the transaction history of Bitcoin, but with the course of time it has seen great potential to be applied in other areas due to the properties it offers. The blockchain provides an immutable distributed database based on a growing sequence of blocks. These blocks, being public, form an open system that enhances trust based on the transparency and robustness of the blockchain construction technique. The system, although open, is also semi-anonymous: users identify themselves with public keys (pseudonyms), not with their real identities.

This database can be shared by a large number of users on a \emph{peer-to-peer} basis and allows information to be stored in an immutable and orderly manner. The information added to the blockchain is public, can be accessed at any time by any user of the network and can only be added to the blockchain if there is an agreement between the majority of the parties. After a certain period of time, it can be assumed that the information added to a block can no longer be modified (immutability).

By design, this system intrinsically provides tolerance to node failures, robustness against manipulation and transparency, since it is public.

\section{Etherum}

\chapter{Practical Part}
\toComplete

\chapter{Discussion}
\toComplete

\chapter{Conclussion}
\toComplete

\chapter{Summary}
\toComplete

\chapter{Lists}
\toComplete

\chapter{Glossary (optional)}
\toComplete

\chapter{Appendix (optional)}
\toComplete

%
% Hier beginnen die Verzeichnisse.
%
\clearpage
\printbibliography
\clearpage
% Das Abbildungsverzeichnis
\listoffigures
\clearpage

% Das Tabellenverzeichnis
\listoftables
\clearpage

% Das Quellcodeverzeichnis
\listofcode
\clearpage

\phantomsection
\addcontentsline{toc}{chapter}{\listacroname}
\chapter*{\listacroname}
\begin{acronym}[XXXXX]
    \acro{ABC}[ABC]{Alphabet}
    \acro{WWW}[WWW]{world wide web}
    \acro{ROFL}[ROFL]{Rolling on floor laughing}
\end{acronym}

%
% Hier beginnt der Anhang.
%
\clearpage
\appendix
\end{document}
